---
title: "Milestone 5"
author: "Molly Chiang"
date: "10/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(readr)
library(knitr)
library(janitor)
library(dplyr)
library(tidyverse)

```

```{r}
ny_data <- read_csv("ny_listings.csv")
london_listings <- read_csv("listings.csv")

total_data <- full_join(ny_data, london_listings, by=c("id", "name", "host_id", "host_name", "neighbourhood", "latitude", "longitude", "room_type", "price", "minimum_nights", "number_of_reviews", "last_review", "reviews_per_month", "calculated_host_listings_count", "availability_365"))

```

### Draft About Page

About 250 words of text is typical. Assume I don't know anything about your topic. Explain it to me. What is the data? What is the context? What do the variables mean? Where did you get the data from? 

Airbnb is a San Francisico based company founded in 2008. The company operates through a website and app that allows users to arrange and offer lodging. Guests can 

This data is ____. The data is available for free from the Airbnb 

  

